Supplementary Materials: Constructing Statistical Deformable Models with Shape Flow

### 2015-04-29 supplementary.tex
Another Draft
Supplementary Material Final

\begin{figure}[h!]
\centering
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0000}
    \end{subfigure}
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0001}
    \end{subfigure}
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0010}
    \end{subfigure}
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0015}
    \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0016}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0028}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0031}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0032}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0001}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0003}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0006}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0008}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0009}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0016}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0020}
    % \end{subfigure}
    % \begin{subfigure}[b]{0.115\textwidth}
    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0023}
    % \end{subfigure}
\caption{dAAMs Dense Grid Visualisation.}
\label{fig:fr}
\end{figure}

The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks. There are four experiments reported to support applications of dAAMs. Experiment \ref{sec:fittingresults} exhibits a full fitting visualisations of non-rigid face and ear alignment in-the-wild between classic AAMs and our dense AAMs. Experiments \ref{sec:modelanalysis} compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches.
Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation with corresponding evaluations on precision.

@@

This section provided additional visualisation results of experiments in original paper section 3.3 Non-rigid object alignment in-the-wild, where quantitative analysis of dense AAMs of ears and faces are shown. Although there are few figures demonstrated normalise point-to-point error measure of ear fitting, only sparse points are shown in order to maintain readability. But here we have visualisation of pixel-wise dense fitting results for both faces and ears. Results for this experiment of faces are reported over the 224
testing images of the LFPW database using 68 point ground truth landmark annotations\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}. For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper. Results for fitting ears are reported over 105 testing images.

Figure \ref{fig:fr} shows dense fitting results in grid view, thus dense points are visualisible without affecting the visibility of appearance.

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear}
        \caption{dAAMs Fitting on Faces}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.2\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_test}
        \caption{dAAMs Fitting on Ears}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam}
        \caption{AAMs Fitting on Faces}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.2\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam_test}
        \caption{AAMs Fitting on Ears}
    \end{subfigure}
    \caption{Final Fitting Statistics of dAAMs and AAMs on Faces}
    \label{fig:rc_face}
\end{figure}

@@

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_aam_eigen_shape}
        \caption{AAMs Variance Ratio on Ears}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_of_eigen_shape}
        \caption{dAAMs Variance Ratio on Ears}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_aam_eigen_shape}
        \caption{AAMs Variance Ratio on Faces}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_of_eigen_shape}
        \caption{dAAMs Variance Ratio on Faces}
    \end{subfigure}
    \caption{AAMs Variance Ratio}
    \label{fig:compact}
\end{figure}

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
    \caption{Caricatures Appearance Reconstruction}
    \label{fig:draw}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/ear}
        \caption{Ear Initial Bounding Box}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle}
        \caption{Bottle Initial Bounding Box}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body}
        \caption{Body Initial Bounding Box}
    \end{subfigure}
    \caption{Perturb Initialisation of Object Detector}
    \label{fig:seg_init}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle_seg}
        \caption{Precision Measure of Bottles}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_jump_seg}
        \caption{Precision Measure of Jumping Action}
    \end{subfigure}
    \qquad
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_slide_seg}
        \caption{Precision Measure of Sliding Action}
    \end{subfigure}
    \caption{Precision Measure on Segmentation}
    \label{fig:seg_result}
\end{figure}

In this section, we experimenting on utilising our dense AAM for objects segmentation. Two subjects, bottles and human, are involved. As for human segmentation, we gather ground true images from Space-Time Actions\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}\cite{ActionsAsSpaceTimeShapes_iccv05]}, where several human action sequences are provided with segmentation. There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames. For bottles, 500 high resolution images of bottles are collected and annotated using not only a newly defined 50 point annotation scheme for bottles, but also the curve annotations proposed in this paper. We randomly split the previous database into two disjoint sets of training (400) and testing (100) images. Bottle models were built using 400 training images while body models are built in terms of human actions (e.g. jumping), each having approximately 200 training images and 50 test images. Note here that we used the same procedures used in experiment \ref{sec:fittingresult} to build models.

Fitting dAAMs on test images gives dense landmarks which could be used to perform segmentation. A simple object detector would be required in prior to our pipeline to initialise the fitting. For simple evaluation, we perturb the ground-truth segmentation with certain variance to simulate an object detector with implicit detection. Initialisation samples are shown in Figure \ref{fig:seg_init}. The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Figure \ref{fig:seg_result}, where statistical results including mean, variance and median are presented.

>>>>

The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks. There are four experiments reported to support applications of dAAMs. Experiment \ref{sec:fittingresults} exhibits a full fitting visualisations of non-rigid face and ear alignment in-the-wild between classic AAMs and our dense AAMs. Experiments \ref{sec:modelanalysis} compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches.
Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation.

@@

This section provided additional visualisation results of experiments in original paper section 3.3 Non-rigid object alignment in-the-wild, where quantitative analysis of dense AAMs of ears and faces are shown. Although there are few figures demonstrated normalise point-to-point error measure of ear fitting, only sparse points are shown in order to maintain readability. But here we have visualisation of pixel-wise dense fitting results for both faces and ears. Results for this experiment of faces are reported over the 224 testing images of the LFPW database using 68 point ground truth landmark annotations
\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}. 
For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper. Results for fitting ears are reported over 105 testing images.

Figure \ref{fig:fr} shows dense fitting results in grid view, thus dense points are visualisible without affecting the visibility of appearance. Full fitting results visualisation are provided in supplementary videos.

\begin{figure}[!t]
\centering
\includegraphics[width=0.45\textwidth]{supports/Fittings/fittings}
\caption{dAAMs Dense Grid Visualisation.}
\label{fig:fr}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{supports/Models/models}
\caption{First Five Principle Components Visualisation of dAAMs on Ears and Faces}
\label{fig:pcamodel}
\end{figure*}

@@

\begin{figure}[!b]
    \centering
    \vspace*{-0.1in}
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_daams}
        %\caption{dAAMs dense shape reconstruction}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_aams}
        %\caption{AAMs dense shape reconstruction}
    \end{subfigure}
    \caption{Dense Shape Reconstruction}
    \label{fig:rc_face}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
    \caption{Caricatures Appearance Reconstruction}
    \label{fig:draw}
\end{figure}

@@

Figure \ref{fig:pcamodel} demonstrated shape and appearance models visualisation for dense AAMs of ears and faces. Middle column shows mean shape and mean appearance while rest columns present corresponding principle components with $\pm 3$ variance.

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/variance_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumulative_variance_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{dAAMs vs AAMs Variance Ratios}
    \label{fig:compact}
\end{figure}

@@

\begin{table}[!b]
\small
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
\hline\hline
Bottles         & 0.8125      & 0.1460     & 0.8414\\
Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
\hline
\end{tabular}
\caption{Segmentation statistics for experiment \ref{sec:segmentation}}
\label{tab:seg_result}
\end{table}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
        %\caption{Ear Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
        %\caption{Bottle Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
        %\caption{Body Initial Bounding Box}
    \end{subfigure}
    \caption{Perturb Initialisation of Object Detector}
    \label{fig:seg_init}
\end{figure}

In this section, we experimenting on utilising our dense AAM for objects segmentation. Two subjects, bottles and human, are involved. As for human segmentation, we gather ground true images from Space-Time Actions
\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}},
where several human action sequences are provided with segmentation. There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames. For bottles, 500 high resolution images of bottles are collected and annotated using not only a newly defined 50 point annotation scheme for bottles, but also the curve annotations proposed in this paper. We randomly split the previous database into two disjoint sets of training (400) and testing (100) images. Bottle models were built using 400 training images while body models are built in terms of human actions (e.g. jumping), each having approximately 200 training images and 50 test images. Note here that we used the same procedures used in experiment \ref{sec:fittingresults} to build models.

Fitting dAAMs on test images gives dense landmarks which could be used to perform segmentation. A simple object detector would be required in prior to our pipeline to initialise the fitting. For simple evaluation, we perturb the ground-truth segmentation with certain variance to simulate an object detector with implicit detection. Initialisation samples are shown in Figure \ref{fig:seg_init}. The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Table \ref{tab:seg_result}, where statistical results including mean, variance and median are presented.
